Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-14 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Added Miragoli2016 in SSCM part

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014}, for investigating
the differentiation of stem cells \cite{Gorelik2008} and the correlation of
topography and T-tubule distribution in cardiomyocytes \cite{Lyon2012} during
recovery from heart failure. Furthermore, it has been utilized in studies
investigating endocytotic pathways \cite{Shevchuk2008}
(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged clathrin
light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated
endocytosis revealed the effect of mutations in the Dynamin~2 gene on the
maturation and internalisation of clathrin coated pits \cite{Ali2019}.

>>>>

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014}, for investigating
the differentiation of stem cells \cite{Gorelik2008} and the correlation of
topography and T-tubule distribution \cite{Lyon2012} or topography and
mitochondria localization and appearance \cite{Miragoli2016} in healthy and 
heart-failure cardiomyocytes. Furthermore, it has been utilized in 
studies investigating endocytotic pathways \cite{Shevchuk2008}
(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged clathrin
light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated
endocytosis revealed the effect of mutations in the Dynamin~2 gene on the
maturation and internalisation of clathrin coated pits \cite{Ali2019}.
